\documentclass[%
 reprint,
 amsmath,amssymb,
 aps,
]{revtex4-1}

\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math

\begin{document}


\title{How to Write an Outline}% Force line breaks with \\
\thanks{Notes of \em{Whitesides' Group: Writing a Paper} }%

\author{Determine the authors}



\begin{abstract}
Do not write abstract until the end.

\end{abstract}

\maketitle



\section{\label{introduction}Introduction}

Introduction should be written down during the outline phase.


\begin{enumerate}
    \item Objectives
    \item Motivation
    \item Background
    \item Highlight: What should the reader pay attention to?
    \item Summary: What should the reader expect as a conclusion?
\end{enumerate}


\section{\label{background}Background}

\section{\label{results}Results and Discussions}


\begin{itemize}
\item Collect the key points and results.
\item Place figures and plots in the right order.
\item Show important results first.
\end{itemize}


George Whitesides addressed some writing styles.\cite{Whitesides2004}

\begin{enumerate}
    \item Put a noun right after the word \em{this}.
    \item Experimental results always past tense.
    \item When comparing, put the two objects being compared explicitly in one sentence.
\end{enumerate}



\section{\label{conclusion}Conclusion}

\begin{itemize}
    \item Do not repeat what is in the results section.
    \item Higher level discussions.
    \item Show significance of this paper.
\end{itemize}



\medskip

\begin{thebibliography}{9}
\bibitem{Whitesides2004}
Whitesides, G. M.
\textit{Whitesides' Group: Writing a Paper}.
Advanced Materials, 16(8):1375--1377, 2004.
\end{thebibliography}




\end{document}
